---
title: 'Data Analysis Assignment #1 (50 points total)'
author: "lastName, firstName"
output:
  html_document: default
---

```{r setup, include = FALSE}
# DO NOT ADD OR REVISE CODE HERE
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)

```


Submit both the .Rmd and .html files for grading. You may remove the instructions and example problem above, but do not remove the YAML metadata block or the first, "setup" code chunk.  Address the steps that appear below and answer all the questions. Be sure to address each question with code and comments as needed.  You may use either base R functions or ggplot2 for the visualizations.

-----

The following code chunk will:

(a) load the "ggplot2", "gridExtra" and "knitr" packages, assuming each has been installed on your machine,
(b) read-in the abalones dataset, defining a new data frame, "mydata,"
(c) return the structure of that data frame, and
(d) calculate new variables, VOLUME and RATIO.

Do not include package installation code in this document. Packages should be installed via the Console or 'Packages' tab. You will also need to download the abalones.csv from the course site to a known location on your machine. Unless a *file.path()* is specified, R will look to directory where this .Rmd is stored when knitting.

```{r analysis_setup1, message = FALSE, warning = FALSE}

# a) Load the ggplot2 and gridExtra packages.

library(ggplot2)
library(gridExtra)
library(knitr)
library(magrittr)
library(dplyr)
library(tidyverse)
library(RColorBrewer)

# b) Use read.csv() to read the abalones.csv into R, assigning the data frame to "mydata."

mydata <- read.csv("abalones.csv", sep = ",", stringsAsFactors = TRUE)


# c) Use the str() function to verify the structure of "mydata." You should have 1036 observations
# of eight variables.

str(mydata)

# d) Define two new variables, VOLUME and RATIO. Use the following statements to define VOLUME and
# RATIO as variables appended to the data frame "mydata."

mydata$VOLUME <- mydata$LENGTH * mydata$DIAM * mydata$HEIGHT
mydata$RATIO <- mydata$SHUCK / mydata$VOLUME

```

-----

### Test Items starts from here - There are 6 sections - Total 50 points

***##### Section 1: (6 points) Summarizing the data.***

(1)(a) (1 point) Use *summary()* to obtain and present descriptive statistics from mydata.  Use *table()* to present a frequency table using CLASS and RINGS. There should be 115 cells in the table you present.  

```{r Part_1a}

summary(mydata)

table(mydata$CLASS, mydata$RINGS)

```

**Question (1 point):  Briefly discuss the variable types and distributional implications such as potential skewness and outliers.**

***Answer: (It seems that many of these numeric values are distributed centrally. We see little difference between median and mean for LENGTH, DIAM, HEIGHT, WHOLE, SHUCK, RINGS, VOLUME, RATIO. This indicates that there isn't much skew in either the left or right direction for these features. After doing some back of the napkin math, you can see that the 1st quartile and third quartile values are approximately equidistant from the mean/median for the features listed above. This implies that the features are normally distributed. For outliers, I used the 1.5*IQR method to determine that there are outliers in the following features: lower bound LENGTH, lower bound DIAM, upper bound WHOLE, upper bound SHUCK, upper and lower bound RINGS, upper bound VOLUME, upper bound RATIO. For SEX and CLASS, we do not see an even distribution. The purpose of the study is to predict age of the abalones, but there are nearly 3x as many abalones in the A3 class to use then in the A1 class. I would imagine that having an equal number of samples in each class would be the most helpful. Additionally, we do not see an even distribution among SEX.Nearly 1/3 of the samples are infants which is likely not representative of the population, and there are not an equal number of females and males. )***

(1)(b) (1 point) Generate a table of counts using SEX and CLASS. Add margins to this table (Hint: There should be 15 cells in this table plus the marginal totals. Apply *table()* first, then pass the table object to *addmargins()* (Kabacoff Section 7.2 pages 144-147)).  Lastly, present a barplot of these data; ignoring the marginal totals.  

```{r Part_1b}

addmargins(table(mydata$SEX, mydata$CLASS))

colors = brewer.pal(3, "Set1") 

barplot(table(mydata$SEX, mydata$CLASS),
        beside = TRUE,
        legend = levels(mydata$SEX),
        col = colors)
        

```

**Essay Question (2 points):  Discuss the sex distribution of abalones.  What stands out about the distribution of abalones by CLASS?**

***Answer: (I am curious as to how abalone in age classes A3, A4, and A5 can be considered 'Infant'. These classifications call into question the validity of the data. The assignment background calls out that 'At the completion of the breeding season sexing abalone can be difficult'. This leads me to believe that researchers are not just classifying infant abalone as I but also adult abalones sampled after the breeding season where determining sex is a challenge. It would be better to have a 4th class in the SEX category called 'adult - unknown' or to remove indeterminate adult samples rather than incorrectly classify data. In classes A1, A2, and A3 we see a higher number of males classified than females. It must be easier to classify males than females at a young age, but this leads to our sample being imbalanced from a SEX perspective. )***

(1)(c) (1 point) Select a simple random sample of 200 observations from "mydata" and identify this sample as "work." Use *set.seed(123)* prior to drawing this sample. Do not change the number 123. Note that *sample()* "takes a sample of the specified size from the elements of x." We cannot sample directly from "mydata." Instead, we need to sample from the integers, 1 to 1036, representing the rows of "mydata." Then, select those rows from the data frame (Kabacoff Section 4.10.5 page 87). 

Using "work", construct a scatterplot matrix of variables 2-6 with *plot(work[, 2:6])* (these are the continuous variables excluding VOLUME and RATIO). The sample "work" will not be used in the remainder of the assignment. 

```{r Part_1c}

set.seed(123)
work = mydata[sample(1:nrow(mydata),200,replace = FALSE),]

plot(work[, 2:6])
```

-----

***##### Section 2: (5 points) Summarizing the data using graphics.***

(2)(a) (1 point) Use "mydata" to plot WHOLE versus VOLUME. Color code data points by CLASS.

```{r Part_2a}

ggplot(mydata, aes(x = mydata$VOLUME, y = mydata$WHOLE, colour = mydata$CLASS)) +
  geom_point() +
  xlab("Volume") +
  ylab("Whole Weight") +
  ggtitle("Whole Weight in grams | Volume in cm^3") +
  labs(colour = "Class")

```


(2)(b) (2 points) Use "mydata" to plot SHUCK versus WHOLE with WHOLE on the horizontal axis. Color code data points by CLASS. As an aid to interpretation, determine the maximum value of the ratio of SHUCK to WHOLE.  Add to the chart a straight line with zero intercept using this maximum value as the slope of the line. If you are using the 'base R' *plot()* function, you may use *abline()* to add this line to the plot. Use *help(abline)* in R to determine the coding for the slope and intercept arguments in the functions. If you are using ggplot2 for visualizations, *geom_abline()* should be used.

```{r Part_2b}

shuck_whole_ratio = mydata$SHUCK / mydata$WHOLE

ggplot(mydata, aes(x = WHOLE, y = SHUCK, colour = CLASS)) +
  geom_point() +
  xlab("Whole Weight") +
  ylab("Shuck Weight") +
  ggtitle("Shuck Weight in grams | Whole Weight in grams") +
  labs(colour = "Class") +
  geom_abline(intercept = 0, slope = max(shuck_whole_ratio))


```

**Essay Question (2 points):  How does the variability in this plot differ from the plot in (a)?  Compare the two displays.  Keep in mind that SHUCK is a part of WHOLE.  Consider the location of the different age classes.**

***Answer: (There is less variability in SHUCK:WHOLE than in WHOLE:VOLUME. We see that as both shuck weight and whole weight increase across all age classes that they generally tend to both increase in a linear fashion without a significant deviance from the average. It is worth noting that as the A5 class's whole weight increases the shuck weight increases less, causing many samples in A5 to appear on the underside of the general trend. As we see volume and whole weight increase across all age classes, we see more significant variability from the average. We see this variation occur most frequently in A2, A3, A4, and A5. It is intriguing that while there is little variance in classes A2 and A3 within SHUCK:WHOLE, there is variance within those classes in WHOLE:VOLUME. This generally leads me to believe that shuck weight is a better indicator of whole weight rather than volume. Intuitively, this makes sense based on how the experiment was set up. VOLUME was determined by multiplying length by width and height; this is simply an approximation. A better way to measure WOLUME would have been to use the water displacement method, i.e. put each abalone in a beaker and measure the increase in volume within the beaker. The method taken to measure volume did not account for any oddities in an individual abalone's dimensions such as longer or shorter than average height, etc. )***

-----

***### Section 3: (8 points) Getting insights about the data using graphs.***

(3)(a) (2 points) Use "mydata" to create a multi-figured plot with histograms, boxplots and Q-Q plots of RATIO differentiated by sex. This can be done using *par(mfrow = c(3,3))* and base R or *grid.arrange()* and ggplot2. The first row would show the histograms, the second row the boxplots and the third row the Q-Q plots. Be sure these displays are legible.  

```{r Part_3a}

histogram = ggplot(mydata, aes(x = RATIO, fill = SEX)) +
  facet_grid(~SEX) +
  geom_histogram() +
  ylab("Frequency") +
  xlab("Ratio") +
  labs(colour = mydata$SEX)

boxplot = ggplot(mydata, aes(y = RATIO, fill = SEX)) +
  facet_grid(~SEX) +
  geom_boxplot() +
  ylab("Frequency") +
  xlab("Ratio") 

qqplot = ggplot(mydata, aes(sample = RATIO, colour = SEX)) +
  stat_qq() +
  stat_qq_line(colour = "black") +
  facet_grid(~SEX) +
  ylab("Sample Quantiles") +
  xlab("Theoretical Quantiles") +
  xlim(-3,3)

grid.arrange(histogram, boxplot, qqplot, nrow = 3)
  

```

**Essay Question (2 points): Compare the displays.  How do the distributions compare to normality? Take into account the criteria discussed in the sync sessions to evaluate non-normality.**

***Answer: (It can be determined that non-normally distributed data is shown in a Quantile Quantile plot when the data points form a curve rather than following the trendline. THe data here is fairly normally distributed but outliers, especially among female and infant samples, cause some non-normality at the ends. This is reinforced by the Boxplots and Histograms which show outliers and a right skew in the datasets, respectively.)***

(3)(b) (2 points) The boxplots in (3)(a) indicate that there are outlying RATIOs for each sex. *boxplot.stats()* can be used to identify outlying values of a vector. Present the abalones with these outlying RATIO values along with their associated variables in "mydata". Display the observations by passing a data frame to the kable() function. Basically, we want to output those rows of "mydata" with an outlying RATIO, but we want to determine outliers looking separately at infants, females and males.

```{r Part_3b}

outliers_ratio_f = boxplot.stats(mydata$RATIO[mydata$SEX == "F"], coef = 1.5)$out
outliers_ratio_i = boxplot.stats(mydata$RATIO[mydata$SEX == "I"], coef = 1.5)$out
outliers_ratio_m = boxplot.stats(mydata$RATIO[mydata$SEX == "M"], coef = 1.5)$out

outliers_ratio = c(outliers_ratio_f, outliers_ratio_i, outliers_ratio_m)

kable(mydata[mydata$RATIO %in% outliers_ratio,])
```

**Essay Question (2 points):  What are your observations regarding the results in (3)(b)?**

***Answer: (We can see that there were the most outliers removed from I, second most from F and last from M. While I am still suspicious of the infant data's validity, the outliers appear to be on the lower bound which indicate that those outliers are abnormally small infant samples, rather than unclassifiable adults. I think that it's interesting that most of the adult outlier samples are in A3. I guess that abalones either hit a physical peak and then begin to shrink or their size peaks in A3 and that is when they are fished out of the wild. The latter scenario is backed up by 1b where we see fewer samples in A4 and A5. This is either because abalone are naturally dying in A3, or being taken away.)***

-----

***### Section 4: (8 points) Getting insights about possible predictors.***

(4)(a) (3 points) With "mydata," display side-by-side boxplots for VOLUME and WHOLE, each differentiated by CLASS There should be five boxes for VOLUME and five for WHOLE. Also, display side-by-side scatterplots:  VOLUME and WHOLE versus RINGS. Present these four figures in one graphic:  the boxplots in one row and the scatterplots in a second row. Base R or ggplot2 may be used.


```{r Part_4a}

box_volume_class = ggplot(mydata, aes(y = VOLUME, x = CLASS)) +
  geom_boxplot() +
  ylab("Volume") +
  xlab("Class")
 
box_whole_class = ggplot(mydata, aes(y = WHOLE, x = CLASS)) +
  geom_boxplot() +
  ylab("Whole") +
  xlab("Class")

scatter_volume_rings = ggplot(mydata, aes(y = VOLUME, x = RINGS)) +
  geom_point()

scatter_whole_rings = ggplot(mydata, aes(y = WHOLE, x = RINGS)) +
  geom_point()


grid.arrange(box_volume_class, box_whole_class, scatter_volume_rings,
             scatter_whole_rings, nrow = 2, ncol = 2)

```

**Essay Question (5 points) How well do you think these variables would perform as predictors of age?  Explain.**

***Answer: (Overall, one of these would be good but using both would be pointless. I'll explain. VOLUME and WHOLE features have nearly identical profiles when being measured against either age class or rings. The volume of a specific sample will give you the exact same information to predict that sample's age class as the whole weight of that same sample would. Using both of these features in a model may marginally improve performance in a best case scenario but also puts the model at risk of overfitting. Now I'll examine how VOLUME and WHOLE predict age. They do not predict RINGS well. This looks like a graph that displays two variables with little correlation. Each ring value has incredibly large WHOLE and VOLUME ranges. And these ranges overlap greatly from one ring count to another. Age class, on the other hand, may be an effective tool to predict infants versus adults. In age classes A3, A4, and A5 there is significant overlap in VOLUME and WHOLE range from one age class to another. However, A1 and A2 have little overlap with each other, A3 or beyond. Reclassify the target variables to get the most out of volume/whole as predictors of age. Make the age class categories A1, A2, and Other. Both volume and whole would be effective at predicting those classes. Without changing the age classes, VOLUME and WHOLE remain effective for predicting samples in A1 and A2, as well. )***

-----

***### Section 5: (12 points) Getting insights regarding different groups in the data.***

(5)(a) (2 points) Use *aggregate()* with "mydata" to compute the mean values of VOLUME, SHUCK and RATIO for each combination of SEX and CLASS. Then, using *matrix()*, create matrices of the mean values. Using the "dimnames" argument within *matrix()* or the *rownames()* and *colnames()* functions on the matrices, label the rows by SEX and columns by CLASS. Present the three matrices (Kabacoff Section 5.6.2, p. 110-111). The *kable()* function is useful for this purpose.  You do not need to be concerned with the number of digits presented.

```{r Part_5a}

mean_volume = aggregate(VOLUME ~ SEX + CLASS, mydata, mean)
mean_shuck = aggregate(SHUCK ~ SEX + CLASS, mydata, mean)
mean_ratio = aggregate(RATIO ~ SEX + CLASS, mydata, mean)


kable(matrix(round(mean_volume$VOLUME, 2), nrow = 3, byrow = FALSE,
                dimnames = list(unique(levels(mydata$SEX)),
                unique(levels(mydata$CLASS)))), caption = "VOLUME")

kable(matrix(round(mean_shuck$SHUCK, 2), nrow = 3, byrow = FALSE,
                dimnames = list(unique(levels(mydata$SEX)),
                unique(levels(mydata$CLASS)))), caption = "SHUCK")

kable(matrix(round(mean_ratio$RATIO, 2), nrow = 3, byrow = FALSE,
                dimnames = list(unique(levels(mydata$SEX)),
                unique(levels(mydata$CLASS)))), caption = "RATIO")
```

(5)(b) (3 points) Present three graphs. Each graph should include three lines, one for each sex. The first should show mean RATIO versus CLASS; the second, mean VOLUME versus CLASS; the third, mean SHUCK versus CLASS. This may be done with the 'base R' *interaction.plot()* function or with ggplot2 using *grid.arrange()*.

```{r Part_5b, fig.width = 9}

ratio_v_class = aggregate(RATIO ~ CLASS+SEX, mydata, mean)
volume_v_class = aggregate(VOLUME ~ CLASS+SEX, mydata, mean)
shuck_v_class = aggregate(SHUCK ~ CLASS+SEX, mydata, mean)

ratio_class = ggplot(ratio_v_class, aes(y = RATIO, x = CLASS, group = SEX, colour = SEX)) +
  geom_point(size = 10) +
  geom_line()

volume_class = ggplot(volume_v_class, aes(y = VOLUME, x = CLASS, group = SEX, colour = SEX)) +
  geom_point(size = 10) +
  geom_line()

shuck_class = ggplot(shuck_v_class, aes(y = SHUCK, x = CLASS, group = SEX, colour = SEX)) +
  geom_point(size = 10) +
  geom_line()

grid.arrange(ratio_class, volume_class, shuck_class, ncol = 1)

```

**Essay Question (2 points):  What questions do these plots raise?  Consider aging and sex differences.**

***Answer: (These plots once again beg the question: why are there infants classified in age groups A3, A4, and A5? We also see that male samples have a significant gain in both SHUCK and VOLUME from A1 to A2, whereas female samples seem to be more fully grown at a younger age. This observation should be taken with a grain of salt, if the infant samples in the A1 class are in fact mostly female then the current trend on display may shift. In 1b we saw that the vast majority of samples in A1 are infant rather than male or female. The actual sex of the samples would likely shift this visualization significantly. I think that it's interesting how as abalones age, the ratio of SHUCK:VOLUME decreases. Seems like these animals grow into their shell size over their lifetime. This observation also calls into question the method for gathering volume by approximating length, height and width rather than calculating volume of a sample through displacement.)***

5(c) (3 points) Present four boxplots using *par(mfrow = c(2, 2)* or *grid.arrange()*. The first line should show VOLUME by RINGS for the infants and, separately, for the adult; factor levels "M" and "F," combined. The second line should show WHOLE by RINGS for the infants and, separately, for the adults. Since the data are sparse beyond 15 rings, limit the displays to less than 16 rings. One way to accomplish this is to generate a new data set using subset() to select RINGS < 16.  Use ylim = c(0, 1100) for VOLUME and ylim = c(0, 400) for WHOLE.  If you wish to reorder the displays for presentation purposes or use ggplot2 go ahead.

```{r Part_5c}

infant_under_16_rings = subset(mydata, RINGS < 16 & SEX == "I")
nrow(infant_under_16_rings)
#322

adult_under_16_rings = subset(mydata, ((RINGS < 16) & (SEX == "M" | SEX == "F")))
nrow(adult_under_16_rings)
#649

infant_volume = ggplot(infant_under_16_rings, aes(fill = RINGS, y = VOLUME)) +
  facet_grid(~RINGS) +
  ylim(0,1100) +
  xlab("Rings") +
  ylab("Volume") +
  ggtitle("Infant Volume | Rings") +
  geom_boxplot(color ="black", fill = "light blue") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())

adult_volume = ggplot(adult_under_16_rings, aes(fill = RINGS, y = VOLUME)) +
  facet_grid(~RINGS) +
  ylim(0,1100) +
  xlab("Rings") +
  ylab("Volume") +
  ggtitle("Adult Volume | Rings") +
  geom_boxplot(color ="black", fill = "dark red") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())

infant_weight = ggplot(infant_under_16_rings, aes(fill = RINGS, y = WHOLE)) +
  facet_grid(~RINGS) +
  ylim(0,400) +
  xlab("Rings") +
  ylab("Whole Weight") +
  ggtitle("Infant Whole Weight | Rings") +
  geom_boxplot(color ="black", fill = "light blue") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())

adult_weight = ggplot(adult_under_16_rings, aes(fill = RINGS, y = WHOLE)) +
  facet_grid(~RINGS) +
  ylim(0,400) +
  xlab("Rings") +
  ylab("Whole Weight") +
  ggtitle("Adult Whole Weight | Rings") +
  geom_boxplot(color ="black", fill = "dark red") +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())

grid.arrange(infant_volume, adult_volume, infant_weight, adult_weight, nrow = 2, ncol = 2)

```

**Essay Question (2 points):  What do these displays suggest about abalone growth?  Also, compare the infant and adult displays.  What differences stand out?**

***Answer: (As discussed in 4a, VOLUME and WHOLE are nearly identical specifically when the target variable is RINGS. For infants, we see nearly step wise growth for WHOLE and VOLUME up to 9 rings, then 10 and beyond is where things level off. For adults, we see that the samples begin to overlap in their VOLUME and WHOLE ranges by RINGS much earlier, around 4. This leads me to believe that abalone growth is linear in the infant stage and then begins to vary in the adult stage. It is likely that abalone early development is the same across the population but then once adulthood is reached some abalone continue growing while others remain the same WHOLE and VOLUME. We could also be seeing the leveling off in the adult population because of the fact that adults are fished out of the habitat.)***

-----

***### Section 6: (11 points) Conclusions from the Exploratory Data Analysis (EDA).***


**Conclusions**


**Essay Question 1) (5 points)	Based solely on these data, what are plausible statistical reasons that explain the failure of the original study? Consider to what extent physical measurements may be used for age prediction.**

***Answer: ( There simply isn't a feature called out in this study that can accurately determine age across all CLASS and RINGS. VOLUME, SHUCK, and WHOLE can at best do a good job separating infants from adults, but we see across these features that once a sample is in CLASS A3, the ability to differentiate breaks down. I believe a remedy for this would be to correctly classify SEX. As noted in the problem statement, SEX can be hard to determine after the breeding season and for young samples. 5b shows that there is a gap between average SHUCK and VOLUME values for males and females persistent across CLASS. Had samples where sex is indeterminate but age is above a certain threshold been discarded, this could create a more clear distinction and allow for VOLUME, SHUCK, and/or WHOLE to more accurately classify the age of adult samples broken down by SEX. I also think that it is entirely possible that for an organism such as an abalone, physical measurements may not be able to provide a detailed enough age profile of an individual sample. Perhaps the study should have found ways to determine age outside of the organism's physical traits. If this study were used to determine age of humans, physical traits such as hair color, wrinkle presence, and other features could be used. It is possible that abalone, being less complexed organisms, have fewer features that can be used to determine age. Maybe something to look at beyond physical features would be the conditions of an abalone's shell. As an abalone ages, it is likely that it's shell chemistry is affected by being in salt water for a longer period of time. Maybe creating a feature that accounted for this would have helped determine samples age as they reached adulthood.)***

**Essay Question 2) (3 points) Do not refer to the abalone data or study.  If you were presented with an overall histogram and summary statistics from a sample of some population or phenomenon and no other information, what questions might you ask before accepting them as representative of the sampled population or phenomenon?**

***Answer: (If I had no ability to understand the greater context of the dataset beyond the histogram and summary statistics, I would look for the data to be normally distributed without skew. I would examine the mean versus median and determine that they are equal. I would use the empirical rule to validate the correct amounts of data are within the appropriate distance from the mean. Finally, I would use the 1.5(IQR) method to ensure that there is not a significant presence of outliers, a significant amount of outliers could mean that the sample is not an accurate representation of the population.)***

**Essay Question 3)  (3 points)	Do not refer to the abalone data or study.  What do you see as difficulties analyzing data derived from observational studies? Can causality be determined?  What might be learned from such studies?**

***Answer: (I believe that there are three significant issues with observational studies that call their accuracy into question: 1 - trust in accuracy of the target variable. 2 - accuracy of the measurements. 3 - comprehensiveness of measurements taken. The importance of being able to trust the accuracy of the target variable cannot be overstated. Without an accurately measured target variable, your entire study can be invalid. Target variables can be measured inaccurately most frequently when the target is subject to interpretation or as the number of outcomes increases. For example, I once built a predictive model to determine whether or not a patient was on the autism spectrum. The significant presence of false positives and negatives in the target variable, a binary yes/no, made building an accurate model challenging. The accuracy of the predictor variables also sways the robustness of a predictive model. If a study fails to call out caveats in the data, does not effectively handle NA's, or takes a poor approach at measuring a predictor then it can be a challenge to build a model with high confidence. Finally, if an observational study does not take a comprehensive approach to gathering a significant number of predictor variables, and ensuring that a large enough sample is taken of each, then a modeler will have their hands tied. An observational study should measure a large number of predictors from various segments to ensure a dataset is created that can be used for in depth analysis. A place where I personally feel that observational studies excel is determining causality. I think that this is because observational studies are often run by team of researchers with deep domain expertise. Where observational studies lack is in their statistical underpinnings and data governance, as described above. I find that determining causality transcends the ability to perform a robust statistical analysis. Domain context and knowledge is necessary to determine why one feature causes a certain outcome versus another that may have a similar correlation value. Where the strength of a data scientist without domain expertise drops off, the expertise of a researcher with domain knowledge picks up. )***
